Basic Analysis of Simplex output

### 2017-03-09 tools/analyses/Rmd/BasicAnalysis.Rmd
modified model.py, bide.py, and randparam.py to ensure that non-fluid movement is modeled -KL
added overhauled modeling code -KL

# Replacing 0's with 1's to allow log-transforms below
simplex.dat <- simplex.dat[complete.cases(simplex.dat), ]

@@

phys.dat <- as.matrix(subset(simplex.dat, 
                      select = c(flow.rate,
                                 barriers,
                                 width,
                                 height,
                                 amplitude)))

>>>>

simplex.dat <- simplex.dat[complete.cases(simplex.dat), ]
simplex.dat$tau <- (simplex.dat(width)*simplex.dat(height))/simplex.dat(flow.rate)

@@

phys.dat <- as.matrix(subset(simplex.dat, 
                      select = c(tau
                                 flow.rate,
                                 barriers,
                                 width,
                                 height,
                                 amplitude)))
